% The format (A5) is selected to facilitate reading on small
% devices and should NOT be changed. 
\documentclass[a5paper,10pt,oneside]{article}

% The package babel is loaded for Swdish with Swedish hyphenation,
% replaces "Contents" with "Innehållsförteckning, "References"
% with "Litteraturförteckning", etc.
\usepackage[swedish]{babel}

\usepackage[T1]{fontenc}

% The package "inputenc" lets us specify what character encoding
% has been used to save the .tex file. If your computer runs
% Linux, the encoding is probably "utf8" by default, while under
% Windows the default will probably be "latin1" The wrong
% character encoding may give strange signs instead of "å", "ä"
% and "ö" or may result in compilation errors.

%\usepackage[latin1]{inputenc} % Probably right if you use Windows
\usepackage[utf8]{inputenc}  % Probably right if you use Linux

% The packages listed below are optional and can be removed if you
% don't use them 
\usepackage{graphicx} 
\usepackage{cite}
\usepackage{url}
\usepackage{ifthen}
\usepackage{listings}	

% These two lines set up options for the listings package and
% can be removed if you don't use it, or changed if you, e.g, 
% use another language than Java. 
% For more information about the listings package see:
% ftp://ftp.tex.ac.uk/tex-archive/macros/latex/contrib/listings/listings.pdf
\def \lstlistingname {Kodexempel}
\lstset{language=Java,tabsize=3,numbers=left,frame=L,floatplacement=hbtp}


\usepackage{ifpdf}
\ifpdf
	\usepackage[hidelinks]{hyperref}
\else
	\usepackage{url}
\fi


% Change NR and TITLE below to appropriate values
\title{Tema NR: 7 GRAFER}

% Write the name and user namn for all participants in the group here.
% Separate persons with \and
\author{Oscar Törnquist \url{osta3589} \and Emil Rosell \url{emro9957}}




\begin{document}

\maketitle

% Here the actual report starts. Everything from here to the start of the
% bibilography should, of course, be removed before you start writing your 
% own text.

\section*{Muntafrågor}
\begin{enumerate}
\item Förklara vad som menas med att en graf är viktad. För VG, ange vilken algoritm som används för att hitta den kortaste vägen i en viktad graf, samt hur den fungerar.
\item Förklara skillnaden mellan djup-först-sökning och bredd-först-sökning. För VG, förklara ingående hur de båda sökningarna fungerar, samt ge exempel på situationer där de används.
\item Förklara för- och nackdelar med kopplingsmatriser. För VG,kontrastera kopplingsmatriser med en annan implementationsmetod.
\item Förklara varför Dijkstra's algortim inte fungerar med negativa värden för bågar. För VG, diskutera hur man ska göra för att komma fram till rätt svar utan Dijkstra's algoritm.
\item Förklara skillnaden mellan en oriktad och en riktad graf. För VG, förklara vilka problem som kan uppstå med riktade grafer och diskutera för och nackdelar mellan dom olika sorterna.
\item Förklara vad som menas med minimum spanning tree. För VG, diskutera dom två algoritmerna som nämns i boken angående minimum spanning tree.

\end{enumerate}





\end{document}
